Fake Clicks on Video Ads

### 2015-05-05 doc/paper.tex
finalized paper

Aside from the view counts, this service also offered to generate comments on YouTube video. This website claims to offer 24/7 customer support via emails and also chat services. The chat services didn't seems to work as no one replied when we started to use their chat service screen. Moreover, when we sent an email asking about their basic operation on March 2, 2015, we didn't receive any reply as of April 2$^{nd}$, 2015. However, when we purchase their service of 1000 views for 3 dollars, we did receive a confirmation email from socialwarehouseorg@gmail.com with the name ``Kevin M''.

@@

\begin{figure}
  \centering
  \includegraphics[width=3.0in]{fig3a}
  \caption{``About'' page of SocialWarrior.net}
\end{figure}

@@

Again, we are assuming YouTube view counting system checks source public IP address since this information could be used to detect bot traffic. A video with 1000 views should have multiple public source IP addresses since users are geographically separated and use different ISPs. Although many users share same publish IP address, it is highly unlikely that all 1000 real views came from one public IP address out of 4 billion. Therefore, we used Amazon’s instances to incorporate 5 different IP addresses when executing our artificial view count generating code.

@@

Fake view on video advertisement is relatively new; thus, not many published research are available. However, there is a researched conducted by Cornell University, where they partnered with Tencent Video and were able to collect much data on real video advertisements~\cite{c5}. They came up with the idea to calculate entropy value base on captured traffic. It distinguishes real and bot traffic based on the entropy value where lower the number, it more likely a bot. The authors stated that
their entropy value system was 98\% accurate distinguishing real to fake views on video advertisements~\cite{c5}; thus, we assume YouTube is using a similar system. As mentioned before, YouTube stops the count at 301 views and analyzes the traffic before granting any more view counts. This closely fits into the Cornell’s entropy system, where captured traffic is carefully analyzed to distinguish between real and fake views on video advertisements.

Similar research was done by UC San Diego, University of Texas, and Microsoft where they focused to catching spam clicks on online advertisements~\cite{c18}. This research used around 10 ethical publishers as a baseline to calculate the Return On Investment (ROI) value, then assume that spam clickers have higher ROI value~\cite{c18}. This research is interesting since it focuses the heart of the issue where money derived from artificial views create incentives for hackers.

>>>>

Aside from the view counts, this service also offered to generate comments on YouTube video. This website claims to offer 24/7 customer support via emails and also chat services. The chat services didn't seems to work as no one replied when we started to use their chat service screen. Moreover, when we sent an email asking about their basic operation on March 2, 2015, we didn't receive any reply as of April 4$^{th}$, 2015. However, when we purchase their service of 1000 views for 3 dollars, we did receive a confirmation email from socialwarehouseorg@gmail.com with the name ``Kevin M''.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in]{fig3a}
  \caption{``About'' page of SocialWarrior.net}
\end{figure}

@@

Again, we are assuming YouTube view counting system checks source public IP address since this information could be used to detect bot traffic. A video with 1000 views should have multiple source IP addresses since users are geographically separated and use different ISPs. Although many users share same publish IP address, it is highly unlikely that all 1000 real views came from one public IP address out of 4 billion. Therefore, we used Amazon’s instances to incorporate 5 different IP addresses when executing our artificial view count generating code.

@@

Fake view on video advertisement is relatively new; thus, not many published research are available. However, there is a research conducted by Cornell University, where they partnered with Tencent Video and were able to collect much data on real video advertisements~\cite{c5}. They came up with the idea to calculate entropy value base on captured traffic. It distinguishes real and bot traffic based on the entropy value where lower the number, it more likely a bot. The authors stated that
their entropy value system was 98\% accurate distinguishing real to fake views on video advertisements~\cite{c5}; thus, we assume YouTube is using a similar system. As mentioned before, YouTube stops the count at 301 views and analyzes the traffic before granting any more view counts. This closely fits into the Cornell’s entropy system, where captured traffic is carefully analyzed to distinguish between real and fake views on video advertisements.

Similar research was done by UC San Diego, University of Texas, and Microsoft where they focused on catching spam clicks on online advertisements~\cite{c18}. This research used around 10 ethical publishers as a baseline to calculate the Return On Investment (ROI) value, then assume that spam clickers have higher ROI value~\cite{c18}. This research is interesting since it focuses the heart of the issue where money derived from artificial views create incentives for hackers.
